gij bent 2

### 2024-12-09 paper/paper.qmd
Add Geeraerts reference to lects
Add piece about power law distributions and Barabasi

[^lects]: i.e. "lects", TODO Geeraerts

@@

Another aspect of of the complex-adaptive system of language are the connections between people. Humans are embedded in larger social networks, which are formed according to a so-called "power law". [uitleg scale-free netwerk]
Linguistically, the effects of networks has been studied before [stuk Julie].

>>>>

[^lects]: For example, one of the language varieties or "lects", defined as "dialects, regiolects, national varieties, registers, styles, idiolects, whatever" [@geeraerts_lectal_2005, 168]

@@

Another aspect of of the complex-adaptive system of language are the connections between people. Humans are embedded in larger social networks, which are formed according to a so-called "power law". This means the network has a small number of people with a large number of connections, supplemented by many people who have relatively few connections [@barabasi_emergence_1999].

Linguistically, the effects of networks has been studied before [stuk Julie].
